---
title: "Study 2: Green Market Game Experiment"
subtitle: "Treatment (Republican Twin) vs. Control (Dogs Chatbot)"
date: today
format:
  html:
    code-fold: true
    toc: true
    toc-depth: 3
    fig-cap-location: bottom
    tbl-cap-location: top
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(mongolite)
library(lme4)
library(lmerTest)
library(lavaan)
library(broom)
library(broom.mixed)
library(effectsize)
library(patchwork)
library(gt)

knitr::opts_chunk$set(dpi = 150)

# ── Load .env ────────────────────────────────────────────────────────────────

dotenv::load_dot_env(here::here(".env"))
MONGODB_URI <- Sys.getenv("MONGODB_URI")

# Game parameters
OPTIMAL_REVENUE_PER_ROUND <- 245000  # 50k Harlan + 50k Williamson
N_ROUNDS <- 8

# Colors
COND_COLORS <- c(control = "#9ca3af", treatment = "#2563eb")
COND_LABELS <- c(control = "Control (Dogs)", treatment = "Treatment (Twin)")
MARKET_COLORS <- c(
  harlan = "#dc2626", williamson = "#f97316",
  burlington = "#3b82f6", middlesex = "#1d4ed8"
)

# Helpers
pformat <- function(p, digits = 3) {
  threshold <- 10^(-digits)
  if (is.na(p)) return("NA")
  if (p < threshold) paste0("< .", paste(rep("0", digits - 1), collapse = ""), "1")
  else paste0("= ", sprintf(paste0("%.", digits, "f"), p))
}
```

# Data

```{r pull-data}
con <- mongo(
  collection = "participants",
  db = "synthetic-contact",
  url = MONGODB_URI
)

raw <- con$find("{}")
cat("Total documents:", nrow(raw), "\n")
con$disconnect()
```

```{r clean}
# ── Filter to completed participants ─────────────────────────────────────────

d <- raw |> filter(!is.na(completed_at))
cat("Completed:", nrow(d), "/", nrow(raw), "\n")

# ── Exclude test data (Prolific PIDs starting with "test_") ──────────────────
# Keep test data if that's all we have (for development)

n_real <- sum(!str_starts(d$prolific_pid, "test_"))
if (n_real > 0) {
  d <- d |> filter(!str_starts(prolific_pid, "test_"))
  cat("After excluding test PIDs:", nrow(d), "\n")
} else {
  cat("WARNING: Only test data available. Keeping all", nrow(d), "rows for development.\n")
}

# ── Quality flags ────────────────────────────────────────────────────────────

d <- d |>
  mutate(
    flag_chatbot_duration = !chatbot_duration_valid,
    flag_honeypot = honeypot_value != "" & !is.na(honeypot_value),
    flag_fast_bot = bot_timing_ms < 5000,
    flag_any = flag_chatbot_duration | flag_honeypot | flag_fast_bot
  )

cat("Quality flags:\n")
cat("  Chatbot duration invalid:", sum(d$flag_chatbot_duration, na.rm = TRUE), "\n")
cat("  Honeypot failed:", sum(d$flag_honeypot, na.rm = TRUE), "\n")
cat("  Fast bot timing (<5s):", sum(d$flag_fast_bot, na.rm = TRUE), "\n")
cat("  Any flag:", sum(d$flag_any, na.rm = TRUE), "\n")

# ── Tab leaves ───────────────────────────────────────────────────────────────

d <- d |>
  mutate(
    n_tab_leaves = map_int(tab_leaves, ~ if (is.data.frame(.x)) nrow(.x) else 0L)
  )

# ── Unnest game rounds ──────────────────────────────────────────────────────

rounds <- d |>
  select(submission_id, condition, prolific_pid, extremity, party, game_rounds) |>
  unnest(game_rounds) |>
  mutate(
    alloc_R = alloc_harlan + alloc_williamson,
    alloc_D = alloc_burlington + alloc_middlesex
  )

cat("\nParticipant-level:", nrow(d), "rows\n")
cat("Round-level:", nrow(rounds), "rows\n")
```

```{r descriptives}
#| label: tbl-descriptives
#| tbl-cap: "Sample descriptives by condition"

d |>
  group_by(condition) |>
  summarize(
    N = n(),
    `Age (M)` = mean(age, na.rm = TRUE) |> round(1),
    `Age (SD)` = sd(age, na.rm = TRUE) |> round(1),
    `% Female` = (mean(gender == "Female", na.rm = TRUE) * 100) |> round(0),
    `Extremity (M)` = mean(extremity, na.rm = TRUE) |> round(1),
    `Chat duration (s)` = mean(chatbot_duration_ms / 1000, na.rm = TRUE) |> round(0),
    .groups = "drop"
  ) |>
  gt() |>
  cols_label(condition = "Condition")
```

# Quality Checks

```{r quality}
#| label: tbl-quality
#| tbl-cap: "Quality flag summary"

d |>
  summarize(
    N = n(),
    `Chatbot too short` = sum(flag_chatbot_duration, na.rm = TRUE),
    `Honeypot fail` = sum(flag_honeypot, na.rm = TRUE),
    `Bot timing < 5s` = sum(flag_fast_bot, na.rm = TRUE),
    `Any flag` = sum(flag_any, na.rm = TRUE),
    `Median tab leaves` = median(n_tab_leaves, na.rm = TRUE)
  ) |>
  gt()
```

# Primary Analysis: Condition → % Allocated to R Markets

**Hypothesis**: Treatment participants allocate more budget to Republican-leaning markets because the chatbot corrected their overestimation of Republican hostility toward environmental products.

```{r primary}
#| label: fig-primary
#| fig-cap: "% of total budget allocated to Republican-leaning markets by condition"

# Descriptives by condition
d |>
  group_by(condition) |>
  summarize(M = mean(game_total_pct_R, na.rm = TRUE),
            SD = sd(game_total_pct_R, na.rm = TRUE),
            N = n(), .groups = "drop") |>
  print()

# Need >= 2 per cell for t-test
cell_ns <- d |> count(condition)
can_infer <- all(cell_ns$n >= 2)

if (can_infer) {
  tt <- t.test(game_total_pct_R ~ condition, data = d)
  cd <- cohens_d(game_total_pct_R ~ condition, data = d)
  cat(sprintf("t(%.1f) = %.2f, p %s, d = %.2f\n",
              tt$parameter, tt$statistic, pformat(tt$p.value), cd$Cohens_d))
} else {
  cat("Too few participants per cell for inference. Showing descriptives only.\n")
}

# Regression (need >= 2 per cell)
if (can_infer) {
  m1 <- lm(game_total_pct_R ~ condition, data = d)
  m2 <- lm(game_total_pct_R ~ condition + extremity + age + gender, data = d)
} else {
  m1 <- m2 <- NULL
}

# Plot
d |>
  ggplot(aes(x = condition, y = game_total_pct_R, fill = condition)) +
  geom_boxplot(alpha = 0.4, outlier.shape = NA, width = 0.5) +
  geom_jitter(width = 0.15, alpha = 0.5, size = 2) +
  stat_summary(fun = mean, geom = "point", shape = 18, size = 4, color = "black") +
  scale_fill_manual(values = COND_COLORS, labels = COND_LABELS, guide = "none") +
  scale_x_discrete(labels = COND_LABELS) +
  labs(x = NULL, y = "% Budget to R-Leaning Markets (Total)") +
  theme_minimal(base_size = 14)
```

```{r primary-table}
#| label: tbl-primary
#| tbl-cap: "OLS: Condition predicting total % allocated to R-leaning markets"

if (!is.null(m1)) {
  bind_rows(
    tidy(m1, conf.int = TRUE) |> mutate(model = "Bivariate"),
    tidy(m2, conf.int = TRUE) |> mutate(model = "With covariates")
  ) |>
    filter(term != "(Intercept)") |>
    select(model, term, estimate, std.error, statistic, p.value, conf.low, conf.high) |>
    mutate(across(where(is.numeric), ~ round(.x, 3))) |>
    gt() |>
    cols_label(
      model = "Model", term = "Predictor",
      estimate = "b", std.error = "SE", statistic = "t",
      p.value = "p", conf.low = "95% CI Low", conf.high = "95% CI High"
    )
} else {
  cat("Regression tables will appear once sufficient data is collected.\n")
}
```

# Learning Curve: Condition × Round

Treatment effect should be strongest in early rounds — participants who chatted with a Republican twin start with less biased priors about R-market receptivity.

```{r learning-curve}
#| label: fig-learning-curve
#| fig-cap: "Round-by-round % allocated to R-leaning markets by condition"

# ── Plot ─────────────────────────────────────────────────────────────────────

round_means <- rounds |>
  group_by(condition, round) |>
  summarize(
    M = mean(pct_R, na.rm = TRUE),
    SE = sd(pct_R, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

round_means |>
  ggplot(aes(x = round, y = M, color = condition, fill = condition)) +
  geom_ribbon(aes(ymin = M - SE, ymax = M + SE), alpha = 0.2, color = NA) +
  geom_line(linewidth = 1) +
  geom_point(size = 2.5) +
  scale_color_manual(values = COND_COLORS, labels = COND_LABELS) +
  scale_fill_manual(values = COND_COLORS, labels = COND_LABELS, guide = "none") +
  scale_x_continuous(breaks = 1:N_ROUNDS) +
  geom_hline(yintercept = 100, linetype = "dashed", alpha = 0.3) +
  annotate("text", x = N_ROUNDS, y = 100, label = "Optimal (100% R)",
           hjust = 1, vjust = -0.5, size = 3, alpha = 0.5) +
  labs(
    x = "Round", y = "% Budget to R-Leaning Markets",
    color = NULL
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "top")
```

```{r lmm}
#| label: tbl-lmm
#| tbl-cap: "Mixed-effects model: pct_R ~ condition × round + (1 + round | participant)"

rounds_m <- rounds |>
  mutate(
    round_c = round - 1,  # center at round 1
    cond_t = ifelse(condition == "treatment", 1, 0)
  )

if (n_distinct(rounds_m$submission_id) >= 4) {
  lmm <- lmer(
    pct_R ~ cond_t * round_c + (1 + round_c | submission_id),
    data = rounds_m,
    REML = FALSE
  )

  tidy(lmm, effects = "fixed", conf.int = TRUE) |>
    mutate(across(where(is.numeric), ~ round(.x, 3))) |>
    gt() |>
    cols_label(
      term = "Predictor", estimate = "b", std.error = "SE",
      statistic = "t", p.value = "p",
      conf.low = "95% CI Low", conf.high = "95% CI High"
    )
} else {
  cat("Too few participants for mixed model. Need >= 4.\n")
  lmm <- NULL
}
```

```{r lmm-interpretation}
if (!is.null(lmm)) {
  fe <- fixef(lmm)
  cat("Interpretation:\n")
  cat(sprintf("  Intercept (control, round 1): %.1f%%\n", fe["(Intercept)"]))
  cat(sprintf("  Treatment effect at round 1: %.1f pp\n", fe["cond_t"]))
  cat(sprintf("  Learning rate (control): %.1f pp/round\n", fe["round_c"]))
  cat(sprintf("  Treatment × round interaction: %.1f pp/round\n", fe["cond_t:round_c"]))
}
```

# Market-Level Allocation Over Rounds

```{r market-allocation}
#| label: fig-market-allocation
#| fig-cap: "Mean allocation to each market over rounds, by condition"

market_long <- rounds |>
  pivot_longer(
    cols = c(alloc_harlan, alloc_williamson, alloc_burlington, alloc_middlesex),
    names_to = "market",
    values_to = "allocation",
    names_prefix = "alloc_"
  )

MARKET_LABELS <- c(
  harlan = "Harlan, KY (R78%)", williamson = "Williamson, TN (R72%)",
  burlington = "Burlington, VT (D68%)", middlesex = "Middlesex, MA (D72%)"
)

market_means <- market_long |>
  group_by(condition, round, market) |>
  summarize(M = mean(allocation, na.rm = TRUE), .groups = "drop")

market_means |>
  ggplot(aes(x = round, y = M / 1000, color = market)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 1.5) +
  facet_wrap(~ condition, labeller = labeller(condition = COND_LABELS)) +
  scale_color_manual(values = MARKET_COLORS, labels = MARKET_LABELS) +
  scale_x_continuous(breaks = 1:N_ROUNDS) +
  labs(x = "Round", y = "Mean Allocation ($k)", color = NULL) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom")
```

# Revenue: Does Treatment → More R Allocation → Higher Revenue?

```{r revenue}
#| label: fig-revenue
#| fig-cap: "Cumulative revenue and % of optimal by condition"

p_rev <- d |>
  ggplot(aes(x = condition, y = game_cumulative_revenue / 1000, fill = condition)) +
  geom_boxplot(alpha = 0.4, outlier.shape = NA, width = 0.5) +
  geom_jitter(width = 0.15, alpha = 0.5, size = 2) +
  stat_summary(fun = mean, geom = "point", shape = 18, size = 4) +
  scale_fill_manual(values = COND_COLORS, guide = "none") +
  scale_x_discrete(labels = COND_LABELS) +
  labs(x = NULL, y = "Cumulative Revenue ($k)") +
  theme_minimal(base_size = 14)

p_opt <- d |>
  ggplot(aes(x = condition, y = game_pct_optimal, fill = condition)) +
  geom_boxplot(alpha = 0.4, outlier.shape = NA, width = 0.5) +
  geom_jitter(width = 0.15, alpha = 0.5, size = 2) +
  stat_summary(fun = mean, geom = "point", shape = 18, size = 4) +
  scale_fill_manual(values = COND_COLORS, guide = "none") +
  scale_x_discrete(labels = COND_LABELS) +
  labs(x = NULL, y = "% of Optimal Revenue") +
  theme_minimal(base_size = 14)

p_rev + p_opt

# t-tests (if enough data)
if (can_infer) {
  cat("Revenue:\n")
  t.test(game_cumulative_revenue ~ condition, data = d) |> print()
  cat("\n% Optimal:\n")
  t.test(game_pct_optimal ~ condition, data = d) |> print()
} else {
  d |> group_by(condition) |>
    summarize(M_rev = mean(game_cumulative_revenue), M_opt = mean(game_pct_optimal)) |>
    print()
}
```

## Mediation: Condition → pct_R → Revenue

```{r mediation}
#| label: tbl-mediation
#| tbl-cap: "Mediation: condition → total pct_R → cumulative revenue (bootstrapped)"

d_med <- d |>
  mutate(cond_t = ifelse(condition == "treatment", 1, 0))

med_model <- "
  # a path: condition -> mediator
  game_total_pct_R ~ a * cond_t

  # b path: mediator -> outcome (controlling for condition)
  game_cumulative_revenue ~ b * game_total_pct_R + c_prime * cond_t

  # indirect effect
  indirect := a * b

  # total effect
  total := c_prime + a * b
"

if (nrow(d_med) >= 10) {
  med_fit <- sem(med_model, data = d_med, se = "bootstrap", bootstrap = 1000)
  parameterEstimates(med_fit, boot.ci.type = "perc") |>
    filter(label != "") |>
    select(label, est, se, ci.lower, ci.upper, pvalue) |>
    mutate(across(where(is.numeric), ~ round(.x, 3))) |>
    gt() |>
    cols_label(
      label = "Path", est = "Estimate", se = "SE",
      ci.lower = "95% CI Low", ci.upper = "95% CI High", pvalue = "p"
    )
} else {
  cat("Too few participants for mediation analysis. Need >= 10.\n")
}
```

# Moderators

## Extremity

More extreme Democrats might have stronger (more biased) priors → larger room for the twin to correct.

```{r extremity}
#| label: fig-extremity
#| fig-cap: "Treatment effect on pct_R moderated by political extremity"

if (can_infer) {
  m_ext <- lm(game_total_pct_R ~ condition * extremity, data = d)
  tidy(m_ext, conf.int = TRUE) |>
    mutate(across(where(is.numeric), ~ round(.x, 3))) |>
    gt()
} else {
  cat("Moderation analysis will appear once sufficient data is collected.\n")
}

d |>
  ggplot(aes(x = extremity, y = game_total_pct_R, color = condition)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  scale_color_manual(values = COND_COLORS, labels = COND_LABELS) +
  labs(x = "Political Extremity", y = "% Budget to R Markets", color = NULL) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "top")
```

# Bonus (Real Money)

```{r bonus}
#| label: fig-bonus
#| fig-cap: "Game bonus ($) by condition"

d |>
  ggplot(aes(x = condition, y = game_bonus, fill = condition)) +
  geom_boxplot(alpha = 0.4, outlier.shape = NA, width = 0.5) +
  geom_jitter(width = 0.15, alpha = 0.5, size = 2) +
  stat_summary(fun = mean, geom = "point", shape = 18, size = 4) +
  scale_fill_manual(values = COND_COLORS, guide = "none") +
  scale_x_discrete(labels = COND_LABELS) +
  labs(x = NULL, y = "Bonus ($)") +
  theme_minimal(base_size = 14)

if (can_infer) {
  t.test(game_bonus ~ condition, data = d) |> print()
} else {
  d |> group_by(condition) |> summarize(M_bonus = mean(game_bonus, na.rm = TRUE)) |> print()
}
```

# Round-Level Decision Time

```{r time}
#| label: fig-time
#| fig-cap: "Decision time (seconds) per round by condition"

rounds |>
  ggplot(aes(x = round, y = time_ms / 1000, color = condition)) +
  stat_summary(fun = mean, geom = "line", linewidth = 0.8) +
  stat_summary(fun = mean, geom = "point", size = 2) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  scale_color_manual(values = COND_COLORS, labels = COND_LABELS) +
  scale_x_continuous(breaks = 1:N_ROUNDS) +
  labs(x = "Round", y = "Decision Time (s)", color = NULL) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "top")
```

# Session Info

```{r}
sessionInfo()
```
