---
title: "Learning from AI Twins"
subtitle: "Can marketers learn about consumers across the political divide?"
author: "Benjamin Lira, Noah Castelo, Olivier Toubia, Stefano Puntoni"
date: today
bibliography: '../lit/references.bib'
format:
  beamer:
    incremental: true
    theme: default
    colortheme: default
    fonttheme: default
    aspectratio: 169
    navigation: horizontal
    section-titles: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(arrow)
library(lme4)
library(lmerTest)
library(ggplot2)
library(broom)
library(patchwork)
library(emmeans)
library(effectsize)
library(ggpubr)

# Load data
is_running_in_quarto <- function() {
  return(Sys.getenv("QUARTO_DOCUMENT_PATH") != "")
}

if (is_running_in_quarto()) {
  dat <- read_parquet("../data/processed/analysis_data.parquet")
} else {
  dat <- read_parquet("./data/processed/analysis_data.parquet")
}

# Colors
party_colors <- c("Democrat" = "#0015BC", "Republican" = "#E81B23")
learner_party_colors <- c("D->R" = "#0015BC", "R->D" = "#E81B23")
extremism_colors <- c("High Extremism" = "#FF8C00", "Low Extremism" = "#20B2AA")

# Fix arrow encoding in data
dat <- dat %>%
  mutate(learner_party = case_when(
    learner_party == "D→R" ~ "D->R",
    learner_party == "R→D" ~ "R->D",
    TRUE ~ learner_party
  ))

# Prepare long data
accuracy_long <- dat %>%
  select(ResponseId, learner_party, accuracy_pre, accuracy_post) %>%
  pivot_longer(cols = c(accuracy_pre, accuracy_post), names_to = "time",
               names_pattern = "accuracy_(pre|post)", values_to = "error") %>%
  mutate(time = factor(time, levels = c("pre", "post")))

warmth_long <- dat %>%
  select(ResponseId, learner_party, warmth_outgroup_pre, warmth_outgroup_post) %>%
  pivot_longer(cols = c(warmth_outgroup_pre, warmth_outgroup_post), names_to = "time",
               names_pattern = "warmth_outgroup_(pre|post)", values_to = "warmth") %>%
  mutate(time = factor(time, levels = c("pre", "post")))

# Sample sizes
n_dr <- dat %>% filter(learner_party == "D->R") %>% nrow()
n_rd <- dat %>% filter(learner_party == "R->D") %>% nrow()
```

# Introduction

## Paper Strategy

\begin{center}
\Large
Two-paper plan
\end{center}

\vspace{2em}

\begin{enumerate}
\item \textbf{General science paper first:} Focus on synthetic contact as a tool for reducing political misperceptions and affective polarization

\vspace{1em}

\item \textbf{Marketing-specific paper second:} Apply insights to consumer research and cross-partisan market understanding
\end{enumerate}

## Goals for Today

\begin{center}
\Large
Feedback for today
\end{center}

\vspace{1.5em}

\begin{enumerate}
\item Feedback on \textbf{framing}

\vspace{0.5em}

\item Feedback on \textbf{analyses} of Study 1.

\vspace{0.5em}

\item \textbf{Most important:} Feedback on \textbf{next study to run}
\end{enumerate}

# The Challenge

## A Fragmented Society

\begin{center}
\Large
Political polarization is at historic highs
\end{center}

\vspace{1em}

\begin{itemize}
\item Americans increasingly live in ideological bubbles
\item Cross-partisan friendships are declining
\item Media consumption is siloed by political identity
\item Partisans see each other as enemies, not fellow citizens
\end{itemize}

\vspace{1em}

\begin{center}
\textbf{For marketers:} How do you understand consumers you never interact with?
\end{center}

## Contact Theory: A Classic Solution

\textbf{Allport (1954): Intergroup contact reduces prejudice}

\vspace{0.5em}

\begin{itemize}
\item Meeting outgroup members corrects stereotypes
\item Builds empathy through personal connection
\item Humanizes "the other side"
\end{itemize}

\vspace{1em}

\textbf{Meta-analyses confirm robust effects}
\begin{itemize}
\item Pettigrew \& Tropp (2006): 500+ studies
\item Contact $\rightarrow$ reduced prejudice
\end{itemize}

## But Intergroup Contact Is Fraught

\begin{center}
\Large
Three problems with real-world contact
\end{center}

\vspace{1em}

\begin{columns}[T]
\begin{column}{0.33\textwidth}
\textbf{1. It's rare}
\begin{itemize}
\item Geographic sorting
\item Social media bubbles
\item Self-selection
\end{itemize}
\end{column}

\begin{column}{0.33\textwidth}
\textbf{2. It can backfire}
\begin{itemize}
\item Hostile encounters
\item Confirmation of stereotypes
\item Anxiety and avoidance
\end{itemize}
\end{column}

\begin{column}{0.33\textwidth}
\textbf{3. It's costly}
\begin{itemize}
\item Time and logistics
\item Emotional labor
\item Not scalable
\end{itemize}
\end{column}
\end{columns}

## Computers as Social Actors

\begin{center}
\Large
People treat computers like people
\end{center}

\vspace{1em}

\textbf{Nass \& Reeves (1996): The Media Equation}
\begin{itemize}
\item People apply social rules to machines
\item Politeness, reciprocity, personality attribution
\item Even when they know it's "just a computer"
\end{itemize}

\vspace{1em}

\textbf{With modern AI:}
\begin{itemize}
\item LLMs can simulate authentic conversations
\item Chatbots can represent diverse perspectives
\item Opens new possibilities for "synthetic" social contact
\end{itemize}

## Synthetic Contact: Does It Work?

\begin{center}
\Large
\textbf{Research Question}
\end{center}

\vspace{1em}

\begin{center}
Can brief interactions with an AI chatbot\\
representing a political outgroup\\
improve understanding and reduce prejudice?
\end{center}

\vspace{2em}

\begin{center}
\textit{Hermann et al. (2025): Synthetic contact shows promise...\\
but questions remain about mechanisms and boundary conditions}
\end{center}

# The Pilot

## Participants

```{r political-dist, fig.height=3, fig.width=6}
p <- dat %>%
  ggplot(aes(politicalorientation_1)) +
  geom_histogram(aes(fill = after_stat(x)), bins = 20) +
  labs(x = 'Political Orientation\n(0 = Strong Democrat, 100 = Strong Republican)',
       y = "Count",
       title = paste0("N = ", nrow(dat), " participants (", n_dr, " Democrats, ", n_rd, " Republicans)")) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, face = "bold", size = 11)) +
  scale_fill_gradient2(low = party_colors["Democrat"],
                       mid = "gray40",
                       high = party_colors["Republican"],
                       midpoint = 50)
p
```

\small
Recruited via Qualtrics panels. Prescreened with partisanship filter.

## The Perception Wedge

```{r perception-wedge, fig.height=3.5, fig.width=9}
# Panel 1: Republicans - actual vs. perceived by Democrats
rep_actual <- dat %>% filter(participant_party == "Republican") %>% pull(green_own)
rep_perceived <- dat %>% filter(participant_party == "Democrat") %>% pull(green_outgroup_pre)

# Calculate effect size for Democrats' misperception of Republicans
dem_outgroup_actual <- mean(rep_actual)
dem_outgroup_perceived <- mean(rep_perceived)
dem_outgroup_d <- (dem_outgroup_perceived - dem_outgroup_actual) / sd(rep_perceived)

rep_data <- tibble(
  value = c(rep_actual, rep_perceived),
  measure = rep(c("Actual", "Perceived by Democrats"), c(length(rep_actual), length(rep_perceived)))
)

p1 <- ggplot(rep_data, aes(x = value, linetype = measure)) +
  geom_density(color = party_colors["Republican"], fill = party_colors["Republican"],
               alpha = 0.2, linewidth = 1) +
  scale_linetype_manual(values = c("solid", "dashed"), name = NULL) +
  labs(x = "Green Attitudes (1-5)", y = "Density",
       title = paste0("Republicans (d = ", sprintf("%.2f", dem_outgroup_d), ")")) +
  theme_minimal(base_size = 12) +
  annotate(geom = 'text', x = c(3.5, 1.8), y = .55, label = c("Actual", "Perceived"), size = 3.5) +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, face = "bold"))

# Panel 2: Democrats - actual vs. perceived by Republicans
dem_actual <- dat %>% filter(participant_party == "Democrat") %>% pull(green_own)
dem_perceived <- dat %>% filter(participant_party == "Republican") %>% pull(green_outgroup_pre)

# Calculate effect size for Republicans' misperception of Democrats
rep_outgroup_actual <- mean(dem_actual)
rep_outgroup_perceived <- mean(dem_perceived)
rep_outgroup_d <- (rep_outgroup_perceived - rep_outgroup_actual) / sd(dem_perceived)

dem_data <- tibble(
  value = c(dem_actual, dem_perceived),
  measure = rep(c("Actual", "Perceived by Republicans"), c(length(dem_actual), length(dem_perceived)))
)

p2 <- ggplot(dem_data, aes(x = value, linetype = measure)) +
  geom_density(color = party_colors["Democrat"], fill = party_colors["Democrat"],
               alpha = 0.2, linewidth = 1) +
  scale_linetype_manual(values = c("solid", "dashed"), name = NULL) +
  labs(x = "Green Attitudes (1-5)", y = "Density",
       title = paste0("Democrats (d = ", sprintf("%.2f", rep_outgroup_d), ")")) +
  theme_minimal(base_size = 12) +
  annotate(geom = 'text', x = c(4.2, 3.8), y = c(.6, .45), label = c("Actual", "Perceived"), size = 3.5) +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, face = "bold"))

p1 + p2
```

\begin{center}
Both groups underestimate outgroup's environmental concern---but Democrats' error is far larger
\end{center}

## Baseline Bias

```{r bias-distribution, fig.height=3, fig.width=6}
# Calculate effect size for baseline accuracy difference between parties
baseline_acc_d <- cohens_d(accuracy_pre ~ participant_party, data = dat, pooled_sd = FALSE)$Cohens_d

dat %>%
  ggplot(aes(x = accuracy_pre, fill = participant_party)) +
  geom_density(color = NA, alpha = 0.6) +
  scale_fill_manual(values = party_colors, name = NULL) +
  labs(x = "Baseline Accuracy (higher = more accurate)", y = "Density",
       title = paste0("Democrats are less accurate than Republicans (d = ", sprintf("%.2f", baseline_acc_d), ")")) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5, face = "bold"))
```

\small
Accuracy = negative absolute difference between perceived and actual outgroup attitudes.

## Baseline Warmth

```{r baseline-warmth, fig.height=3, fig.width=5}
warmth_baseline <- dat %>%
  select(participant_party, warmth_outgroup_pre) %>%
  group_by(participant_party) %>%
  summarise(
    mean_warmth = mean(warmth_outgroup_pre, na.rm = TRUE),
    se_warmth = sd(warmth_outgroup_pre, na.rm = TRUE) / sqrt(n())
  )

ggplot(warmth_baseline, aes(x = participant_party, y = mean_warmth, fill = participant_party)) +
  geom_bar(stat = "identity", alpha = 0.8, width = 0.6) +
  geom_errorbar(aes(ymin = mean_warmth - se_warmth, ymax = mean_warmth + se_warmth), width = 0.2) +
  scale_fill_manual(values = party_colors) +
  labs(x = NULL, y = "Warmth Toward Outgroup (0-100)",
       title = "Baseline Affective Polarization") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, face = "bold")) +
  ylim(0, 100)
```

## The Intervention: 10-Minute AI Conversation

\begin{center}
\includegraphics[height=0.65\textheight]{../materials/qualtrics/screenshots/chatbot.png}

\small
Participants had a 10-minute conversation with an AI chatbot representing their political outgroup's perspective on environmental issues.
\end{center}


# Results

## Main Finding: Accuracy and Warmth Both Improved

```{r main-effects, fig.height=3.5, fig.width=9}
# Calculate summaries
accuracy_summary <- accuracy_long %>%
  group_by(time) %>%
  summarise(mean_val = mean(error, na.rm = TRUE),
            se_val = sd(error, na.rm = TRUE) / sqrt(n()),
            .groups = "drop")

warmth_summary <- warmth_long %>%
  group_by(time) %>%
  summarise(mean_val = mean(warmth, na.rm = TRUE),
            se_val = sd(warmth, na.rm = TRUE) / sqrt(n()),
            .groups = "drop")

# Main effect models
accuracy_model0 <- lmer(error ~ time + (1 | ResponseId), data = accuracy_long)
warmth_model0 <- lmer(warmth ~ time + (1 | ResponseId), data = warmth_long)

acc_d <- -cohens_d(error ~ time, data = accuracy_long, pooled_sd = FALSE)$Cohens_d
warmth_d <- cohens_d(warmth ~ time, data = warmth_long, pooled_sd = FALSE)$Cohens_d

p_acc <- ggplot(accuracy_summary, aes(x = time, y = mean_val)) +
  geom_line(group = 1, linewidth = 1.5, color = "gray30") +
  geom_point(size = 5, color = "gray30") +
  geom_errorbar(aes(ymin = mean_val - se_val, ymax = mean_val + se_val), width = 0.1, color = "gray30") +
  labs(title = paste0("Belief Accuracy (d = ", sprintf("%.2f", acc_d), ")"),
       x = NULL, y = "Accuracy\n(higher = more accurate)") +
  scale_x_discrete(labels = c("Pre", "Post")) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", hjust = 0.5))

p_warmth <- ggplot(warmth_summary, aes(x = time, y = mean_val)) +
  geom_line(group = 1, linewidth = 1.5, color = "gray30") +
  geom_point(size = 5, color = "gray30") +
  geom_errorbar(aes(ymin = mean_val - se_val, ymax = mean_val + se_val), width = 0.1, color = "gray30") +
  labs(title = paste0("Outgroup Warmth (d = ", sprintf("%.2f", warmth_d), ")"),
       x = NULL, y = "Feeling Thermometer (0-100)") +
  scale_x_discrete(labels = c("Pre", "Post")) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", hjust = 0.5))

p_acc + p_warmth
```

\begin{center}
\textbf{Brief AI conversations improved both accuracy and warmth}
\end{center}

## Breaking Down by Party

```{r by-party, fig.height=3.5, fig.width=9}
# Calculate summaries by party
accuracy_summary_party <- accuracy_long %>%
  group_by(learner_party, time) %>%
  summarise(mean_val = mean(error, na.rm = TRUE),
            se_val = sd(error, na.rm = TRUE) / sqrt(n()),
            .groups = "drop")

warmth_summary_party <- warmth_long %>%
  group_by(learner_party, time) %>%
  summarise(mean_val = mean(warmth, na.rm = TRUE),
            se_val = sd(warmth, na.rm = TRUE) / sqrt(n()),
            .groups = "drop")

# Models with interaction
accuracy_model <- lmer(error ~ time * learner_party + (1 | ResponseId), data = accuracy_long)
warmth_model <- lmer(warmth ~ time * learner_party + (1 | ResponseId), data = warmth_long)

# Calculate effect sizes by party
acc_dr_d <- -cohens_d(error ~ time, data = accuracy_long %>% filter(learner_party == "D->R"), pooled_sd = FALSE)$Cohens_d
acc_rd_d <- -cohens_d(error ~ time, data = accuracy_long %>% filter(learner_party == "R->D"), pooled_sd = FALSE)$Cohens_d
warmth_dr_d <- cohens_d(warmth ~ time, data = warmth_long %>% filter(learner_party == "D->R"), pooled_sd = FALSE)$Cohens_d
warmth_rd_d <- cohens_d(warmth ~ time, data = warmth_long %>% filter(learner_party == "R->D"), pooled_sd = FALSE)$Cohens_d

p_acc <- ggplot(accuracy_summary_party, aes(x = time, y = mean_val, color = learner_party, group = learner_party)) +
  geom_line(linewidth = 1.5) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = mean_val - se_val, ymax = mean_val + se_val), width = 0.1) +
  scale_color_manual(values = learner_party_colors, name = NULL) +
  labs(title = paste0("Belief Accuracy\n(D->R: d=", sprintf("%.2f", acc_dr_d), ", R->D: d=", sprintf("%.2f", acc_rd_d), ")"),
       x = NULL, y = "Accuracy (higher = better)") +
  scale_x_discrete(labels = c("Pre", "Post")) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold", hjust = 0.5, size = 10))

p_warmth <- ggplot(warmth_summary_party, aes(x = time, y = mean_val, color = learner_party, group = learner_party)) +
  geom_line(linewidth = 1.5) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = mean_val - se_val, ymax = mean_val + se_val), width = 0.1) +
  scale_color_manual(values = learner_party_colors, name = NULL) +
  labs(title = paste0("Outgroup Warmth\n(D->R: d=", sprintf("%.2f", warmth_dr_d), ", R->D: d=", sprintf("%.2f", warmth_rd_d), ")"),
       x = NULL, y = "Feeling Thermometer (0-100)") +
  scale_x_discrete(labels = c("Pre", "Post")) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold", hjust = 0.5, size = 10))

p_acc + p_warmth + plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

\small
Democrats (D->R) showed larger accuracy gains; warmth increased similarly for both groups.

## Change in Accuracy Correlates with Change in Warmth

```{r acc-warmth-corr, fig.height=3, fig.width=5}
dat_with_changes <- dat %>%
  mutate(
    accuracy_change = accuracy_post - accuracy_pre,
    warmth_change = warmth_outgroup_post - warmth_outgroup_pre
  )

ggplot(dat_with_changes, aes(x = accuracy_change, y = warmth_change, color = learner_party)) +
  geom_point(alpha = 0.3, size = 2, show.legend = FALSE) +
  geom_smooth(method = "lm", se = TRUE, linewidth = 1, show.legend = F) +
  stat_cor(aes(label = paste((..r.label..), ..p.label.., sep = "~`,`~")),
           method = "pearson", show.legend = FALSE, size = 3) +
  scale_color_manual(values = learner_party_colors, name = NULL) +
  facet_wrap(~ learner_party) +
  labs(x = "Accuracy Change (higher = improved)",
       y = "Warmth Change (higher = warmer)") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom")
```

## Does Political Extremity Moderate the Effect?

```{r extremism, fig.height=3.5, fig.width=9}
# Add extremism to long data
accuracy_long_ext <- accuracy_long %>%
  left_join(dat %>% select(ResponseId, political_extremism), by = "ResponseId")

warmth_long_ext <- warmth_long %>%
  left_join(dat %>% select(ResponseId, political_extremism), by = "ResponseId")

# Median split for visualization
extremism_median <- median(dat$political_extremism, na.rm = TRUE)

accuracy_long_ext <- accuracy_long_ext %>%
  mutate(extremism_group = ifelse(political_extremism > extremism_median, "High Extremism", "Low Extremism"))

warmth_long_ext <- warmth_long_ext %>%
  mutate(extremism_group = ifelse(political_extremism > extremism_median, "High Extremism", "Low Extremism"))

# Summaries
acc_ext_summary <- accuracy_long_ext %>%
  group_by(extremism_group, time) %>%
  summarise(mean_val = mean(error, na.rm = TRUE),
            se_val = sd(error, na.rm = TRUE) / sqrt(n()),
            .groups = "drop")

warmth_ext_summary <- warmth_long_ext %>%
  group_by(extremism_group, time) %>%
  summarise(mean_val = mean(warmth, na.rm = TRUE),
            se_val = sd(warmth, na.rm = TRUE) / sqrt(n()),
            .groups = "drop")

p_acc <- ggplot(acc_ext_summary, aes(x = time, y = mean_val, color = extremism_group, group = extremism_group)) +
  geom_line(linewidth = 1.5) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = mean_val - se_val, ymax = mean_val + se_val), width = 0.1) +
  scale_color_manual(values = extremism_colors, name = NULL) +
  labs(title = "Belief Accuracy", x = NULL, y = "Accuracy (higher = better)") +
  scale_x_discrete(labels = c("Pre", "Post")) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold", hjust = 0.5))

p_warmth <- ggplot(warmth_ext_summary, aes(x = time, y = mean_val, color = extremism_group, group = extremism_group)) +
  geom_line(linewidth = 1.5) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = mean_val - se_val, ymax = mean_val + se_val), width = 0.1) +
  scale_color_manual(values = extremism_colors, name = NULL) +
  labs(title = "Outgroup Warmth", x = NULL, y = "Feeling Thermometer (0-100)") +
  scale_x_discrete(labels = c("Pre", "Post")) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold", hjust = 0.5))

p_acc + p_warmth + plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

\begin{center}
\textbf{No moderation:} Even highly polarized individuals benefit equally
\end{center}

## What Drives Learning? Empathy vs. Informativeness

```{r empathy-info, fig.height=3.5, fig.width=9}
dat_for_reg <- dat %>%
  filter(!is.na(accuracy_pre), !is.na(accuracy_post),
         !is.na(warmth_outgroup_pre), !is.na(warmth_outgroup_post),
         !is.na(info), !is.na(empathy)) %>%
  mutate(
    accuracy_change = accuracy_post - accuracy_pre,
    warmth_change = warmth_outgroup_post - warmth_outgroup_pre
  )

p1 <- ggplot(dat_for_reg, aes(x = info, y = accuracy_change, color = learner_party)) +
  geom_jitter(alpha = 0.5, width = 0.2, height = 0, size = 1.5) +
  geom_smooth(method = "lm", se = TRUE) +
  stat_cor(size = 2.5) +
  scale_color_manual(values = learner_party_colors, name = NULL) +
  labs(x = "Bot Informativeness (1-5)", y = "Accuracy Change",
       title = "Informativeness") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "none", plot.title = element_text(face = "bold", hjust = 0.5))

p2 <- ggplot(dat_for_reg, aes(x = empathy, y = accuracy_change, color = learner_party)) +
  geom_jitter(alpha = 0.5, width = 0.2, height = 0, size = 1.5) +
  geom_smooth(method = "lm", se = TRUE) +
  stat_cor(size = 2.5) +
  scale_color_manual(values = learner_party_colors, name = NULL) +
  labs(x = "Bot Empathy (1-5)", y = "Accuracy Change",
       title = "Empathy") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold", hjust = 0.5))

p1 + p2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

\begin{center}
\textbf{Informativeness matters; empathy does not}
\end{center}

## Does Engagement (Dose) Matter?

```{r dose, fig.height=3.5, fig.width=5}
dat_filtered <- dat_for_reg %>%
  mutate(log_word_count = log(user_word_count)) %>%
  filter(user_turn_count <= 75)

ggplot(dat_filtered, aes(x = log_word_count, y = accuracy_change, color = learner_party)) +
  geom_point(alpha = 0.5, size = 1.5) +
  geom_smooth(method = "lm", se = TRUE) +
  stat_cor(size = 3) +
  scale_color_manual(values = learner_party_colors, name = NULL) +
  labs(x = "Log(Word Count)", y = "Accuracy Change\n(higher = improved)") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom")
```

\small
Mixed results: More engagement associated with accuracy gains only for Democrats.

## Confidence Changes

```{r confidence, fig.height=3.5, fig.width=5}
confidence_long <- dat %>%
  select(ResponseId, learner_party, confidence_outgroup_pre, confidence_outgroup_post) %>%
  pivot_longer(cols = c(confidence_outgroup_pre, confidence_outgroup_post),
               names_to = "time", names_pattern = "confidence_outgroup_(pre|post)",
               values_to = "confidence") %>%
  mutate(time = factor(time, levels = c("pre", "post")))

confidence_summary <- confidence_long %>%
  group_by(learner_party, time) %>%
  summarise(mean_conf = mean(confidence, na.rm = TRUE),
            se_conf = sd(confidence, na.rm = TRUE) / sqrt(n()),
            .groups = "drop")

ggplot(confidence_summary, aes(x = time, y = mean_conf, color = learner_party, group = learner_party)) +
  geom_line(linewidth = 1.5) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = mean_conf - se_conf, ymax = mean_conf + se_conf), width = 0.1) +
  scale_color_manual(values = learner_party_colors, name = NULL) +
  labs(x = NULL, y = "Confidence in Outgroup Judgments (1-5)") +
  scale_x_discrete(labels = c("Pre", "Post")) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")
```

\small
Republicans gained confidence despite smaller accuracy gains. Democrats' confidence unchanged.

# Takeaways

## Key Findings

\begin{enumerate}
\item \textbf{Synthetic contact works:} Brief AI conversations improved accuracy and warmth

\vspace{0.5em}

\item \textbf{Asymmetric learning:} Democrats showed larger accuracy gains; warmth increased symmetrically

\vspace{0.5em}

\item \textbf{Extremists benefit too:} Political extremism did not moderate intervention effectiveness

\vspace{0.5em}

\item \textbf{Information > empathy:} Perceived informativeness predicted outcomes; empathy did not

\vspace{0.5em}

\item \textbf{Metacognitive mismatch:} Confidence changes did not track accuracy improvements
\end{enumerate}

## Implications

\textbf{For marketers:}
\begin{itemize}
\item Scalable alternative to focus groups for understanding diverse consumers
\item Particularly valuable for cross-partisan product positioning
\item AI can help bridge the political divide in consumer insights
\end{itemize}

\vspace{1em}

\textbf{For researchers:}
\begin{itemize}
\item Synthetic contact offers new paradigm for reducing intergroup bias
\item Information provision may matter more than emotional connection
\item Metacognitive calibration remains a challenge
\end{itemize}

# Next Steps

## Main Study Design

\textbf{Address key pilot limitations with controlled experiment}

\vspace{0.5em}

\textbf{4-Condition Design (run for both D→R and R→D):}
\begin{enumerate}
\item AI Chatbot (replication)
\item Google Search (practical alternative)
\item Perspective-Taking (gold standard; Wang et al., 2014)
\item Cats/Dogs AI chat (engagement-matched control)
\end{enumerate}

\vspace{0.5em}

\textbf{Sample:} N = 2,000 (250 per cell × 8 cells)

## What We Add

\textbf{1. Control conditions}
\begin{itemize}
\item Google: Practical alternative (but search bias, info quality, effort differ)
\item Perspective-taking: How does AI compare to established intervention?
\item Cats/dogs: Controls for time, engagement, repeated measurement
\end{itemize}

\vspace{1em}

\textbf{2. Longitudinal follow-up}
\begin{itemize}
\item 1-week post-intervention
\item Test durability of accuracy and warmth gains
\item Critical gap: pilot showed immediate effects only
\end{itemize}

## What We Add (cont.)

\textbf{3. Behavioral consequences}
\begin{itemize}
\item \textbf{Conversation willingness}: "How likely would you be to start a conversation with [outgroup] about political issues?" (1-7)
\item \textbf{Partner preference}: "If given opportunity for a conversation about current events, who would you prefer to speak with?" (Dem/Rep/No preference)
\end{itemize}

\vspace{1em}

\textbf{Tests:} Does learning translate to engagement readiness?

## Research Questions

\begin{enumerate}
\item \textbf{Does AI work?} AI vs. cats/dogs control (replication with control)

\vspace{0.5em}

\item \textbf{How does AI compare?} AI vs. Google vs. Perspective-taking

\vspace{0.5em}

\item \textbf{What mechanisms matter?}
  \begin{itemize}
  \item Compare intervention types (exploratory on mechanism)
  \item Google: self-directed search (confounded by search bias, effort)
  \item PT: structured empathy exercise
  \item AI: guided dialogue
  \end{itemize}

\vspace{0.5em}

\item \textbf{Does it last?} Compare immediate vs. 1-week follow-up

\vspace{0.5em}

\item \textbf{Does it change behavior?} Accuracy/warmth → conversation willingness → partner choice
\end{enumerate}

## Questions?

\begin{center}
\Large
Benjamin Lira

\vspace{1em}

\normalsize
\texttt{blira@wharton.upenn.edu}

\vspace{2em}

\small
with Noah Castelo, Olivier Toubia, Stefano Puntoni
\end{center}
